\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliograf\mbox{}ija}

\bibitem{MA} Curt Schimmel:
\textit{UNIX Systems for Modern Arhitectures -\\
Symetric Multiprocessing and Caching for Kernel Programmers}\\
Addison-Wesley; 1994.

\bibitem{APUI} W.~Richard Stevens:
\textit{Advanced Programming in the UNIX Environment}\\
Addison-Wesley; 1992.

\bibitem{UNP} W.~Richard Stevens:
\textit{UNIX NETWORK PROGRAMMING -\\
Networking APIs: Sockets and XTI (Vol.~1)}\\
Prentice-Hall; 1998.

\bibitem{CC} Steve McConnel:
\textit{Code complete}\\
Microsoft Press; 1994.

\bibitem{BE} Bruce Eckel:
\textit{Thinking in C++} (Vol.~1 \& 2, 
2nd
edition)\\
Prentice Hall; 2000.

\bibitem{IZ1} Ivan Zoraja:
\textit{Online Monitoring in Software DSM Systems}\\
(Research Report Series; Vol.~20)\\
LLR-Techniche 
Universit\"{a}t
M\"{u}nchen;
2000.

\bibitem{IZ2} I.~Zoraja, V.~Seitz, A.~Bode, P.~Slapnièar:\\
\textit{Resource Management in Message Passing Environments}\\
(Journal of computing and information technology; Vol.~9, No.~1)\\
University Computing Centre Zagreb; 2001.

\bibitem{SGI}
\textit{Standard Template Library Programmer's Guide}\\
Silicon Graphics Computer Systems; 1996.

\bibitem{MAKE} Richard M.~Stallman 
\& 
Roland McGrath:
\textit{GNU Make}\\
Free Software Foundation; 1999.

\bibitem{EL} Jon Warbrick 
\& 
D.~Carlisle, M.~Goossens, S.~Rahtz, A.~Clark:\\
\textit{Essential 
\LaTeX{}
++}\\
1994.

\bibitem{NSHORT} T. Oetiker, H.~Partl, I.~Hyna 
\& 
E. Schlegl:\\
\textit{The Not So Short Introduction to \LaTeX2e{}}
(Ver.~3.7)\\
Free Software Foundation; 1999.

\end{thebibliography}
